Separating Use and Reuse to Improve Both

### 2017-05-18 FACS/paper.tex

\begin{abstract}
In most object oriented languages subclassing/inheritance implies
subtyping. This is considered by many a conceptual design error, but it
seems required for technical reasons, due to what we call the
\emph{this-leaking problem}, showing that separating
code-reuse from subtyping is non-trivial and requires a significant
departure from the OO models in existing mainstream OO languages.

We are aware of at least 3 independently designed research languages 
that address this limitation:Delta-Trait, Package Template, DeepFjig.

Leveraging on \emph{traits}, in this work we aim to synthesizes
the main ideas of those very different language designs.
Our result is a nominally typed minimalist language, natural to OO programmers.
By making our type system distinguish between code-use and code-reuse
we can separate inheritance and subtyping, while avoiding 
redundant abstract declarations (required in Delta-Trait and DeepFjig), while supporting self construction,
binary methods and recursive types.
Moreover, we provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.

>>>>

\begin{abstract}
In most object oriented languages subclassing/inheritance implies
subtyping. This is considered by many a conceptual design error, but it
seems required for technical reasons, due to what we call the
\emph{this-leaking problem}. The leaking problem shows that separating
code-reuse from subtyping is non-trivial and requires a significant
departure from the OO models in existing mainstream OO languages.
We are aware of at least 3 independently designed research languages 
that address this limitation:Delta-Trait, Package Template, DeepFjig.
Leveraging on \emph{traits}, in this work we aim to synthesizes
the main ideas of those very different language designs.
Our result is a nominally typed minimalist language, natural to OO programmers.
By making our type system distinguish between code-use and code-reuse
we can separate inheritance and subtyping, while avoiding 
redundant abstract declarations (required in Delta-Trait and DeepFjig), while supporting self construction,
binary methods and recursive types.
Moreover, we provide a novel and elegant solution to uniformly
handle behavior and state within trait composition.
